Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
Update paper.tex

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xcolor}
\usepackage{listings}
\lstset{
  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
  numbers=left,
  numberstyle= \tiny,
  keywordstyle= \color{ blue!70},
  commentstyle= \color{red!50!green!50!blue!50},
  frame=single,
  rulesepcolor= \color{ red!20!green!20!blue!20} ,
  escapeinside=``,
  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
  framexleftmargin=2em,
  showstringspaces=false,
  showtabs=false,
  breaklines=true
}
\lstdefinelanguage{Solidity}
{
  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
  morecomment=[l]{//},
  morestring=[b]"
}

@@

\subsection{The Heuristic Search Algorithm}
\label{sec:assembly-algorithm}
Based on the encoding method, we propose a search algorithm based on greedy heuristics in Table~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.

@@

\section{Experiments}
\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}

>>>>

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subfigure} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xcolor}
\usepackage{listings}
\lstset{
  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
  numbers=left,
  numberstyle= \tiny,
  keywordstyle= \color{ blue!70},
  commentstyle= \color{red!50!green!50!blue!50},
  frame=single,
  rulesepcolor= \color{ red!20!green!20!blue!20} ,
  escapeinside=``,
  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
  framexleftmargin=2em,
  showstringspaces=false,
  showtabs=false,
  breaklines=true
}
\lstdefinelanguage{Solidity}
{
  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
  morecomment=[l]{//},
  morestring=[b]"
}

@@

\subsection{The Heuristic Search Algorithm}
\label{sec:assembly-algorithm}
Based on the encoding method, we propose a search algorithm based on greedy heuristics in Algorithm~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.

@@

\section{Experiments}
\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
\paragraph{Clusters.} We perform K-Means on the CDRP control gates of each sample. 
For VGGNet, we generate $1.5$ clusters per class.
Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.

The sample distribution of each cluster is shown in Figure~\ref{fig:vgg-cluster}.

\begin{figure}[!htp]
    \centering
\subfigure[Clusters from VGG-C]{
    \begin{minipage}[t]{1\linewidth}
        \includegraphics[height=1.5in,width=2.8in]{fig/chart1.pdf}
        \label{fig:net2a}
    \end{minipage}
}

    %\vfill
\subfigure[Clusters from VGG-D]{
    \begin{minipage}[t]{1\linewidth}
        \includegraphics[height=1.5in,width=2.8in]{fig/chart2.pdf}
        \label{fig:net2b}
    \end{minipage}
}
    \caption{Sample Distribution of Clusters from Different Types of VGGNets}
    \label{fig:vgg-cluster}

\end{figure}

From Figure~\ref{fig:vgg-cluster}, a cluster from VGG-C typically consists of samples from a single class, which is consistent with the result shown in Figure~\ref{}. 
By contrast, a cluster from VGG-D may contain samples with different labels.

We notice that some clusters only contain extremely few samples such as Cluster-5 so we won't take these clusters into account when choosing classifiers.

\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifer. Each classifier judges whether the test sample should in the corresponding cluster. 
From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline

	\end{tabular}
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
\end{table}

Since we want to get 0/1-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
As a result, each classifer only has $10\%$ parameters of the original full network.

\paragraph{Finetune.} The classifiers we get above cannot achieve any meaningful results because they tend to classifiy all test samples not in the cluster and the weights of the last layer is initialized randomly.
We implement finetune on these classifers to make the results more meaningful and accurate. 
Since the negative samples are greatly more than positive ones in the dataset, we need to implement some strategies to balance them i.e. in each iteration we ensure the ratio of positive and negative samples is about $1:1$ in the batch.

We train each classifer with $1500$ iterations with a batch size $200$. The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$. We only train the pruned model i.e. weights of the pruned channels will remain zero.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
